\TheTitle

### 2017-07-02 paper/results.tex
Results: boxplots for accuracy and time information
Adds boxplots for showing the difference between gitk and Linvis in
timing and accuracy metrics.

All questions from the study, with the exception of the questions
regarding which modules are changed in a merge tree, show conclude with
rejecting the null hypothesis that there is no difference in correctness
when using gitk versus \tool. We do not see a change in these
conclusions if we include continuity correction. Further explanations of
the results are found in the following subsections.

@@

	% McNemar's Chi-squared test

% data:  mat
% McNemar's chi-squared = 15, df = 1, p-value = 0.0001075

           % Linvis
% Gitk        Correct Incorrect
  % Correct         6         0
  % Incorrect      15         2

@@

@@

	% McNemar's Chi-squared test

% data:  mat
% McNemar's chi-squared = 14, df = 1, p-value = 0.0001828

           % Linvis
% Gitk        Correct Incorrect
  % Correct         5         0
  % Incorrect      14         4

@@

@@

	% McNemar's Chi-squared test

% data:  mat
% McNemar's chi-squared = 16, df = 1, p-value = 6.334e-05

           % Linvis
% Gitk        Correct Incorrect
  % Correct         5         0
  % Incorrect      16         2

@@

@@

Further breakdown of this information yielded the following results;
	% McNemar's Chi-squared test

% data:  mat
% McNemar's chi-squared = 13, df = 1, p-value = 0.0003115

           % Linvis
% Gitk        Correct Incorrect
  % Correct         8         0
  % Incorrect      13         2

@@

@@

@@

	% McNemar's Chi-squared test

% data:  mat
% McNemar's chi-squared = 14, df = 1, p-value = 0.0001828

           % Linvis
% Gitk        Correct Incorrect
  % Correct         6         0
  % Incorrect      14         3

@@

@@

	% McNemar's Chi-squared test

% data:  mat
% McNemar's chi-squared = 5.4444, df = 1, p-value = 0.01963

           % Linvis
% Gitk        Correct Incorrect
  % Correct        14         1
  % Incorrect       8         0

@@

% TODO: perform further analysis on this, looking at distance from the
% correct answer, and duration of time taken to answer

>>>>

All questions from the study, with the exception of the questions
regarding which modules are changed in a merge tree, show conclude with
rejecting the null hypothesis that there is no difference in correctness
when using gitk versus \tool. We do not see a change in these
conclusions if we include continuity correction in the McNemar test.
Further explanations of the correctness results are found in the
following subsections.

In Table~\ref{tab:summarization_timing}, we see the timing metrics taken
across all users, and both commits. We then further break the results by
separating the commits by which commit tree it came from in
Table~\ref{tab:summarization_timing_cid}, but do not see tremendous
differences between the commits.

\begin{table}[htpb]
  \centering
  \caption{Summarization task timing in seconds, aggregated over all study participants and both commits}
  \label{tab:summarization_timing}
  \begin{tabular}{r|c|rrr}
    Question                             & Tool   & Median(s) & Mean(s) & Variance(s) \\\hline
    \multirow{2}{*}{Series of Merges}    & Linvis & 8         & 18.1    & 617.5\\
                                         & Gitk   & 37        & 64.4    & 4349.8\\
    \multirow{2}{*}{Other Commits}       & Linvis & 14        & 19.8    & 349.5\\
                                         & Gitk   & 36        & 44.5    & 1471.3\\
    \multirow{2}{*}{Number of Authors}   & Linvis & 1         & 5.7     & 163.3\\
                                         & Gitk   & 11        & 41.5    & 5838.1\\
    \multirow{2}{*}{Biggest Contributor} & Linvis & 3         & 9.4     & 293.0\\
                                         & Gitk   & 11        & 40.9    & 3423.7\\
    \multirow{2}{*}{Number of Files}     & Linvis & 1         & 3.1     & 32.4\\
                                         & Gitk   & 15        & 34.9    & 4143.6\\
    \multirow{2}{*}{Most changed File}   & Linvis & 4         & 15.0    & 959.4\\
                                         & Gitk   & 14        & 48.4    & 3862.0\\
    \multirow{2}{*}{Involved Modules}    & Linvis & 4         & 5.6     & 19.4\\
                                         & Gitk   & 34        & 45.0    & 1703.4
  \end{tabular}
\end{table}

\begin{table*}[htpb]
  \centering
  \caption{Summarization task timings broken down by commit, aggregated over all study participants}
  \label{tab:summarization_timing_cid}
  \begin{tabular}{l|l|rrrr}
    Question                            & Commit & Linvis Median(s) & Gitk Median(s) & Linvis Variance(s) & Gitk Variance(s)\\\hline
    \multirow{2}{*}{Series of Merges}   & \comA  & 8.0              & 37.0           & 437.8              & 3144.5\\
                                        & \comB  & 9.0              & 48.5           & 802.8              & 5707.5\\
    \multirow{2}{*}{Other Commits}      & \comA  & 10.0             & 36.0           & 419.9              & 1513.6\\
                                        & \comB  & 14.5             & 31.0           & 316.3              & 1563.3\\
    \multirow{2}{*}{Number of Authors}  & \comA  & 2.0              & 11.0           & 23.2               & 1668.5\\
                                        & \comB  & 1.0              & 12.0           & 293.0              & 9789.8\\
    \multirow{2}{*}{Biggest Contributor}& \comA  & 2.0              & 6.0            & 1.9                & 2853.2\\
                                        & \comB  & 6.5              & 18.0           & 494.4              & 4154.6\\
    \multirow{2}{*}{Number of Files}    & \comA  & 1.0              & 19.0           & 31.0               & 489.7\\
                                        & \comB  & 1.5              & 8.5            & 36.4               & 7588.3\\
    \multirow{2}{*}{Most changed File}  & \comA  & 3.0              & 21.0           & 5.9                & 5343.4\\
                                        & \comB  & 4.0              & 10.0           & 1652.0             & 2696.0\\
    \multirow{2}{*}{Involved Modules}   & \comA  & 3.0              & 19.0           & 29.5               & 1946.2\\
                                        & \comB  & 4.5              & 39.5           & 12.1               & 1622.8\\
  \end{tabular}
\end{table*}

% We attempt to fit a normal distribution to both the timing and accuracy
% information, but there are not enough samples to accurately assess the
% parameterization of this data; we can see a strong shifted normal
% distribution forming for some questions
% (Figure~\ref{fig:q8_accuracy_density}), but others do not express this
% behaviour (Figure~\ref{fig:q3_accuracy_density}).

% \begin{figure}[htpb]
%   \centering
%   \includegraphics[page=2, width=0.8\linewidth]{figures/userstudy/accuracy/q8.pdf}
%   \caption{Density function compared to the fitted normal distribution,
%     showing the difference in correctness when using Gitk versus \tool
%     counting the number of files involved.
%     Negative values imply that participants were more accurate with
%     Gitk, positive values imply better accuracy with \tool.
%     }
%   \label{fig:q8_accuracy_density}
% \end{figure}

% \begin{figure}[htpb]
%   \centering
%   \includegraphics[page=2, width=0.8\linewidth]{figures/userstudy/accuracy/q3.pdf}
%   \caption{Comparing the density function, plotting the difference in
%     accuracy between responses provided by Gitk and Linvis. Responses
%     are answering the series of merges involved with merging a commit.}
%   \label{fig:q3_accuracy_density}
% \end{figure}

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q3.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for determining
    the series of merges into the master branch of the repository.}
  \label{fig:q3_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q3.pdf}
  \caption{Time comparison between Gitk and \tool, for determining
    the series of merges into the master branch of the repository.}
  \label{fig:q3_timing}
\end{figure}

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q4.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for determining
    other commits in the same merge tree.}
  \label{fig:q4_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q4.pdf}
  \caption{Time comparison between Gitk and \tool, for determining
    other commits in the same merge tree.}
  \label{fig:q4_timing}
\end{figure}

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q5.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering how
  many authors were involved with a merge tree.}
  \label{fig:q5_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q5.pdf}
  \caption{Time comparison between Gitk and \tool, for answering how
  many authors were involved with a merge tree.}
  \label{fig:q5_timing}
\end{figure}

@@

Further breakdown of this information yielded the following results;

@@

There are no accuracy metrics for this question, as the answer is either
correct or incorrect.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q6.pdf}
  \caption{Timing comparison between Gitk and \tool, for answering who
    contributed the most changes.}
  \label{fig:q6_timing}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q7.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering how
  many files were involved with the merge tree.}
  \label{fig:q7_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q7.pdf}
  \caption{Timing comparison between Gitk and \tool, for answering how
    many files were involved with the merge tree.}
  \label{fig:q7_timing}
\end{figure}

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q8.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering
    which file had the most changes.}
  \label{fig:q8_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q8.pdf}
  \caption{Time comparison between Gitk and \tool, for answering which
    file had the most changes.}
  \label{fig:q8_timing}
\end{figure}

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q9.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering
    which modules were involved with a merge.}
  \label{fig:q9_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q9.pdf}
  \caption{Time comparison between Gitk and \tool, for answering which
    modules were involved with a merge.}
  \label{fig:q9_timing}
\end{figure}

% Figure~\ref{fig:q9_accuracy}
